PANCHANGE_data_preprocessing

### 2020-07-23 PANCHANGE_data_preprocessing2020-07-15.Rmd
created gad and pcl missingness chunks

#Missigness of questionnaire items
+++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires

Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

@@

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
```
Missingness for PHQ
```{r phq missingness baseline}
dat.no.sex.no.gender.no.age.no.ibd.phq.base <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na.per.person.phq =
      rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% phq.items_base]))
  )

freq(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)
table(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)

PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
freq(PHQ.cc$miss_pc_total.phq)
```

>>>>

#Missigness of questionnaire items
Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

@@

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
```

PHQ
Complete case data for PHQ baseline (COPING) - 9,260 remaining
```{r complete cases phq base}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_base ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)[1]
```

Complete case data for PHQ pre-pandemic (GLAD) - 37,308 remaining
```{r complete cases phq prepan}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_prepan ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)[1]
```

Complete case data for PHQ retrospective (COPING) - 9,262 remaining
```{r complete cases phq retro}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_retro ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)[1]
```

GAD
Complete case data for GAD baseline (COPING) - 12,457 remaining
```{r complete cases gad base}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_base ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)[1]
```

Complete case data for gad pre-pandemic (GLAD) - 36,149 remaining
```{r complete cases gad prepan}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_prepan ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)[1]
```

Complete case data for gad retrospective (COPING) - 8,930 remaining
```{r complete cases gad retro}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_retro ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)[1]
```

PCL
Complete case data for PCL baseline (COPING) - 12,376 remaining
```{r complete cases pcl base}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_base ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)[1]
```

Complete case data for PCL pre-pandemic (GLAD) - 35,176 remaining
```{r complete cases pcl prepan}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_prepan ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)[1]
```

Complete case data for PCL retrospective (COPING) - 4,618 remaining
```{r complete cases pcl retro}
dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_retro ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)[1]
```
